\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[colorlinks, urlcolor=blue]{hyperref}
\usepackage[letterpaper, margin=.5in]{geometry}

\pagestyle{empty}

% Block paragraphs, no indentation.
\setlength{\parindent}{0em}
\setlength{\parskip}{1.5em}

\begin{document}

\begin{center}
{\Large Logan Schelly}

(951)\phantom{-}692-8802
$\bullet$
idyllogan@verizon.net
\end{center}

\hrule
\bigskip
\noindent14 July 2020
\bigskip

To whom it may concern,
\bigskip

I'm applying for the National Renewable Energy Laboratory's internship 
in Software Development on the High Performance Computing team.
This position has a perfect combination of factors:
I meet the qualifications; 
the work develops skills relevant to my career goals;
and it's in a location I would love to work.
So, how do I meet the qualifications?

First, I'm very comfortable developing in Python.
I recently completed BYU's Applied and Computational Mathematics Emphasis (ACME) and a minor in Computer Science.
Each of the 8 semester-long courses for ACME had an accompanying lab where we
used Python to solve problems and code algorithms related to the concepts we learned in lecture.

Second, I'm accustomed to working in a Linux environment.
The ACME lab machines ran Redhat Linux and the Computer Science machines used KDE Plasma Linux.
When I finally bought a laptop, I installed Ubuntu Linux and I've been using it ever since.
I used an IDE for only two Computer Science classes.
For the rest of them I used a text editor and a Linux terminal.
Furthermore, my systems programming class required us to use C libraries to interact with the Linux kernel.
While I don't know everything about Linux, it's my default working environment;
I'm actually using the terminal, vim, and pdflatex to write this cover letter.

Third, my experiences in ACME and as a math tutor have prepared me with the soft skills you're looking for.
As the head upper division math tutor, I lead and mentored a team of 10 to 20 tutors.
In my senior math courses, several of my assignments were group projects.
This helped me work as an engaged team member.
My work tutoring students and completing mathematics coursework required me to
demonstrate good analytical problem solving skills,
pay close attention to detail, and
effectively communicate technical concepts on paper and in person.

Finally, while I'm no web application expert, I believe I have skills and experiences
that will help me contribute to the web application this internship will focus on.
While I haven't developed a web application before, I have developed an Android application:
my Advanced Programming class project was to write a server and client for displaying family history events on Android devices.
I also have been developing skills with web technologies since graduation.
I've been working through (and contributing to!) the open-source tutorial at
\href{https://javascript.info}{javascript.info} and reading through my roommate's introductory web design book.

Satisfying qualifications makes this a good fit,
but this job in particular has two things that make it a great fit. 

First, this job synergizes excellently with my career goals.
Ultimately, I'd to work on a math software library like Intel's Math Kernel Library or NVIDIA's CUDA.
Working on these libraries requires expertise with computer hardware and parallel algorithms.
I don't have that expertise yet, but working on the High Performance Computing team at the National Renewable Energy Laboratory
seems like the perfect place to develop that expertise

Second, Golden is a great geographic fit.
I grew up in the small town of Idyllwild, California, which is nestled in the San Jacinto Mountain Range.
I did my undergraduate in Provo, Utah, right next to the Wasatch Mountain Range.
I've loved walking 2 miles or less to a trail head, and then hiking above the city.
I feel sense of marvel and accomplishment when I look out over the Earth from a mountain.
Golden has the Rockies in its backyard, giving me tons of opportunities to hike on up and feel at home.

Thank you for your time and consideration.
I look forward to hearing back from you soon.

\bigskip
\noindent Logan Schelly
  
\end{document}
