\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage[letterpaper, margin=.5in]{geometry}
\usepackage[parfill]{parskip} % Remove paragraph indentation
\usepackage{enumitem} % Modify list layouts
\usepackage{tabularx} % Tables the same width as the page.
\usepackage{scrextend} % Add margin environment
\usepackage{amsfonts} % Math symbols
\usepackage{calc} % widthof and length operations (like subtraction)
\usepackage[colorlinks, urlcolor=blue]{hyperref}
\usepackage{multicol}
\usepackage{comment}
\pagestyle{empty} % Suppress page numbers
\setlength{\multicolsep}{0pt} %Prevent multicol from hogging vertical whitespace


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%5555
%My Macros: TODO: move these into a .sty sheet.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%Compact lists TODO: just set these to default.
\newenvironment{compactItemize}{
  \begin{itemize}[itemsep=0ex, parsep=0ex, partopsep=0ex, topsep= -7pt]
}{
  \end{itemize}
}


%Fill with line at text level.
\newcommand{\lineFill}{\leaders\hbox{\rule[.5ex]{1pt}{.1pt}}\hfill}

%Technical Skill Listings
\newcommand{\technicalSkill}[3]{
  \makebox[20ex][l]{#1 \lineFill} 
  #2 \lineFill #3
}
\newenvironment{technicalSkillWithSubskills}[3]{
  \newcommand{\subskill}[1]{\item ##1}
  \technicalSkill{#1}{#2}{#3}
  \smallskip
  \begin{multicols}{4}
  \begin{itemize}[parsep=0ex, partopsep=0ex, topsep=-.7ex, itemsep=-.5ex]
  }{
  \end{itemize}
  \end{multicols}
  \medskip
}

%Job info Listings
\newcommand{\jobInfo}[4]{
  \begingroup
  \setlength{\tabcolsep}{0ex}
  \begin{tabularx}{\linewidth}{X r}
    #1 & % position 
    #2\\ % time range
    #3 & % company
    #4   % location
  \end{tabularx}%
  \endgroup%
}
\newcommand{\degree}[4]{
  % Use same layout as jobInfo
  % Order is degree, grad date, institution, GPA)
  \jobInfo{\textbf{#1}}{#2}{#3}{#4}
}
\newcommand{\project}[2]{
  \begingroup
  \setlength{\tabcolsep}{0ex}
  \begin{tabularx}{\linewidth}{X r}
    #1 & % project name
    #2\\ % time range
  \end{tabularx}%
  \endgroup%
}

\begin{document}

\begin{center}
{\Large Logan Schelly} %Make a \fullName command.

(951)\phantom{-}692-8802 %Make a \phoneNumber{}{}{} command \
$\bullet$ %make a separator commmand.                        |-> Make an essential contact info command.
idyllogan@verizon.net %Make an \email command.              /
\end{center}

\textbf{Work Experience}
\smallskip
\hrule

\jobInfo{Executive Assistant}{Alamo, CA}{Tanius Technology LLC}{Aug 2020 -- Aug 2022}
\begin{compactItemize}
  \item Payroll and 401(k) administration for a company of 35 people.
  \item 
\end{compactItemize}

\jobInfo{Head Upper Division Tutor}{Provo, UT}{BYU Math Lab}{Sep 2014 -- April 2020}
\begin{compactItemize}
  \item Helped students on a first-come first-served basis.
  \item Tutored Linear Algebra, Multivariable Calculus, Differential Equations, and Mathematical Proof classes.
  \item Conducted weekly meetings to help our team of 10-20 upper division tutors prepare for that week's concepts.
  \item Coordinated exam reviews, and often taught them.  10 to 200 students attended, depending on enrollment and subject.
  \item Overhauled the tutor handbook.
  \item Expanded the tutor application test to include a Mathematical Proof section.
\end{compactItemize}
\medskip

\jobInfo{Applied Math TA}{Provo, UT}{BYU Math Department}{Winter 2019}
\begin{compactItemize}
  \item 3 times a week I held office hours to help ACME juniors with their Optimization and Mathematical Analysis homework.
  \item Usually helped between 5 and 10 students.
\end{compactItemize}
\medskip

\jobInfo{Lube Technician}{Provo, UT}{Jiffy Lube}{Summers 2015 and 2016}
\begin{compactItemize}
  \item Serviced up to 50 cars each day.
  \item Changed oil, rotated tires, replaced brake pads, checked and filled under-hood fluids.
  \item Performed basic inspections for wear and tear.
  \item Repaired windshield rock chips.
\end{compactItemize}
\medskip

\jobInfo{AVID Tutor}{Hemet, CA}{Hemet Unified School District}{October 2013 -- April 2014}
\begin{compactItemize}
  \item Worked as a tutor to students in Hemet High School's AVID program.
  \item Mentored groups of 4 to 6 students in any homework assignment they needed help with.
  \item Helped students identify root misunderstandings of concepts, instead of rote memorization.
\end{compactItemize}
\medskip

\jobInfo{Private Tutor}{Hemet, CA}{Self Employed}{September 2012 -- April 2014}
\begin{compactItemize}
  \item Tutored 6 different students individually.  The students were in middle school and high school. 
\end{compactItemize}
\medskip

\jobInfo{Gas Station Clerk}{Idyllwild, CA}{Idyllwild Garage}{Summer 2011 and May 2012 -- January 2013}
\begin{compactItemize}
  \item Depending on the shift, would open or close the store.
  \item Stocked shelves and updated inventory.
  \item Dispensed propane for customers with tanks.
  \item Serviced customers and kept the store clean.
\end{compactItemize}
\medskip

\jobInfo{Landscape Maintenance Crewmember}{K\&M Strategic Management}{Hemet, CA}{Summer 2011 and May 2012 -- January 2013}
\begin{compactItemize}
  \item Leaf-blew the parking lots and picked up trash at managed medical properties every morning.
  \item Weeded, raked, and maintained the landscape at properties.
  \item Cleaned out an empty strip mall in preparation for sale.
  \item Repainted fences, parking lines, and breakrooms.
\end{compactItemize}
\medskip


\textbf{Education}
\smallskip
\hrule

\degree{Bachelors of Science in Mathematics}{April 2020}{Brigham Young University}{GPA: 3.17 out of 4.0}
%
\begin{itemize}[labelindent=2ex, itemsep=0ex, parsep=0ex, partopsep=0ex, topsep= -.7ex]%Need to undo the parskip from usual start
  \item Applied and Computational Mathematics Emphasis (ACME)
  \item Computer Science Minor
  \item Recognized for outstanding performance in Mathematics in 2020 and 2018
\end{itemize}

\begin{addmargin}{2ex}

\textbf{Course Work and Topics}
  \begin{itemize}[labelindent=2ex, parsep=0ex, partopsep=0ex, topsep=-.7ex]
    \item Fundamentals of Mathematics
      \begin{multicols}{4}
        \begin{itemize}[labelindent=2ex, parsep=0ex, partopsep=0ex, topsep=-.7ex]
          \item Set Theory
          \item Logic
          \item Proof Techniques
          \item Relations
          \item Functions
          \item Induction
          \item Cardinality
          \item Number Theory
        \end{itemize}
      \end{multicols}
    \item Linear Algebra
      \begin{multicols}{3}
        \begin{itemize}
          \item Solving Linear Systems
          \item Matrix Algebra
          \item Determinants
          \item Vector Spaces
          \item Eigenvectors
          \item Inner Product Spaces
          \item Quadratic Forms
          \item Singular Value Decomposition
        \end{itemize}
      \end{multicols}
    \item Calculus of Several Variables
      \begin{multicols}{3}
        \begin{itemize}
          \item Quadric Surfaces
          \item Vector Functions
          \item Partial Derivatives
          \item Multiple Integrals
          \item Vector Calculus
        \end{itemize}
      \end{multicols}
    \item Differential Equations
      \begin{multicols}{2}
        \begin{itemize}
          \item First Order Differential Equations
          \item Second Order Linear Differential Equations
          \item Series Solutions of Second Order Equations
          \item Laplace Transformation
          \item Systems of First Order Linear Equations
          \item Numerical Methods
        \end{itemize}
      \end{multicols}
    \item Theory of Analysis
      \begin{multicols}{2}
        \begin{itemize}
          \item Properites of the Real Numbers
          \item Sequences and Series
          \item Topology of $\mathbb{R}$
          \item Limits and Continuity of Functions
          \item Derivatives
          \item Sequences and Series of Functions
          \item Riemann Integration
        \end{itemize}
      \end{multicols}
    \item Mathematical Analysis
      \begin{multicols}{2}
        \begin{itemize}
          \item Abstract Vector Spaces
          \item Linear Transformations and Matrices
          \item Inner Product Spaces
          \item Spectral Theory
          \item Metric Space Topology
          \item Fr\'echet Differentiation
          \item Contraction Mappings
          \item Daniell-Lebesgue Integration
          \item Calculus on Manifolds
          \item Complex Analysis
          \item Spectral Calculus
          \item Iterative Methods for Linear Systems
       \end{itemize}
      \end{multicols}
     \item Algorithm Design and Optimization
      \begin{multicols}{2}
        \begin{itemize}
          \item Measuring Algorithm Complexity
          \item Data Structures
          \item Combinatorial Optimization
          \item Probability
          \item Probabilistic Sampling and Estimation
          \item Random Algorithms
          \item Harmonic Analysis
          \item Polynomial Approximation and Interpoloation
          \item Unconstrained Optimization
          \item Linear Optimization
          \item Nonlinear Constrained Optimization
          \item Convex Analysis and Optimization
          \item Dynamic Optimization
          \item Stochastic Dynamic Optimization
       \end{itemize}
      \end{multicols}
    \item Modeling with Uncertainty and Data
      \begin{multicols}{2}
        \begin{itemize}
          \item Markov Chains
          \item Classical Inference
          \item Hypothesis Testing
          \item Regression and Classification
          \item Bayesian Analysis
          \item Estimation in State Space Models
          \item Machine Learning
          \item Unsupervised Methods
          \item Graphical and Latent Variable Models
          \item Kernel Methods
          \item Tree-Based Methods
        \end{itemize}
      \end{multicols}
    \item Modeling with Dynamics and Control
      \begin{multicols}{2}
        \begin{itemize}
          \item Existence and Uniqueness Theorem
          \item Stability Theory
          \item Bifurcation Theory
          \item Partial Differential Equations
          \item Calculus of Variations
          \item Euler's Equation
          \item Hamilton's Principle
          \item Noether's Theorem
          \item Optimal Control
          \item Pontryagin's Maximum Principle
          \item Linear Quadratic Regulators
        \end{itemize}
      \end{multicols}
  \end{itemize}
\end{addmargin}


\textbf{Skills}
\smallskip
\hrule
\textbf{Programming Languages}
\begin{itemize}[leftmargin=3ex, parsep=1ex, partopsep=0ex, topsep=-.7ex, itemsep=.5ex, label={}]
  \item
  \begin{technicalSkillWithSubskills}
    {Python}
    {Very Comfortable}
    {used in 8 lab classes and 4 lecture classes}
    \subskill{NumPy}
    \subskill{Scipy}
    \subskill{Matplotlib}
    \subskill{SymPy}
    \subskill{Pandas}
    \subskill{scikit-learn}
    \subskill{pytest}
    \subskill{Selenium}
    \subskill{Beautiful Soup}
    \subskill{sqlite3}
  \end{technicalSkillWithSubskills}
  \item
  \begin{technicalSkillWithSubskills}
    {C}
    {Proficient}
    {used in 2 lecture classes}
    \subskill{\texttt{unistd.h}} % fork() execve()
    \subskill{\texttt{signal.h}}  % signal handlers for SIGINT, SIGSTP, etc
    \subskill{\texttt{pthread.h}} % pthread_create() pthread_join()...
    \subskill{\texttt{sys/socket.h}}
    \subskill{\texttt{omp.h} (OpenMP)}
    \subskill{\texttt{regex.h}}
  \end{technicalSkillWithSubskills}
  \item
  \begin{technicalSkillWithSubskills}
    {JavaScript}
    {Beginner}
    {self taught at \href{https://javascript.info}{javascript.info}, and listed as a \href{https://javascript.info/about}{contributor}}
    \subskill{JSON}
    \subskill{Mocha}
    \subskill{Chai}
  \end{technicalSkillWithSubskills}
  \item
  \begin{technicalSkillWithSubskills}
    {Java}
    {Proficient, but rusty}
    {used extensively in 1 lecture class}
    \subskill{GSON}
    \subskill{\texttt{java.sql}}
    \subskill{JUnit}
    \subskill{Android}
  \end{technicalSkillWithSubskills}
  \item \technicalSkill{C++}{Proficient, but rusty}{used in 3 lecture classes}
\end{itemize}

\textbf{Other Tools}
\begin{multicols}{2}
  \begin{compactItemize}
    \item \LaTeX -- Proficient
    \item Spreadsheets -- Proficient
    \item Git -- Intermediate
    \item HTML -- Beginner
  \end{compactItemize}
\end{multicols}

\textbf{Soft Skills}
  \begin{center}
  Tutoring $\bullet$ Attention to Detail $\bullet$ Troubleshooting $\bullet$ Public Speaking $\bullet$ Leadership $\bullet$ Project Coordination
  \end{center}


\textbf{Projects %Of Interest
}
\smallskip
\hrule

\project{Math Lab Student Sign Up Analysis}{Fall 2019 -- Winter 2020}
\begin{compactItemize}
  \item Consolidated data spread across 60+ Excel files.
  \item Used Pandas to analyze the almost 900,000+ instances of students signing up for tutor help.
  \item Identified busiest times of the week, and the topics students most often came in for help with.
  \item Advised scheduling more tutors in the mornings based on my findings.
\end{compactItemize}
\medskip

\project{HTTP Proxy}{Winter 2020}
\begin{compactItemize}
  \item C program that relayed user requests to end server, and relayed server responses to user.
  \item Used \texttt{regex.h} to verify that user requests met HTTP formatting requirements.
  \item Handled concurrent requests with a threadpool using \texttt{pthread.h} and \texttt{semaphore.h}.
\end{compactItemize}
\medskip

\project{DNS Stub Resolver}{Winter 2020}
\begin{compactItemize}
  \item Program interfaced with DNS servers to look up IP addresses associated with a web domain name.
        For example, it would figure out that the domain name www.example.com is associated with IP address 93.184.216.34.
  \item Formatted queries to DNS standards, sent the queries with UDP, and then decoded responses.
  \item Written C with \texttt{unistd.h}, \texttt{sys/socket.h}, \texttt{arpa/inet.h}, and \texttt{netinet/in.h}.
\end{compactItemize}
\medskip

\project{OpenMP with Mandelbrot Set}{Winter 2020}
\begin{compactItemize}
  \item Parallelized the \href{https://gist.github.com/andrejbauer/7919569}{Mandelbrot visualization code} posted on github by Andrej Bauer.
\end{compactItemize}
\medskip

\project{Tiny Shell}{Winter 2020}
\begin{compactItemize}
  \item Wrote a simple shell that could handle process creation, I/O redirection and pipelines, and process control.
  \item Used C with \texttt{unistd.h} and \texttt{signal.h}.
\end{compactItemize}
\medskip

\project{Inverted Pendulum Control}{Winter 2019}
\begin{compactItemize}
  \item Modified the Python code from the CartPole-v1 environment of OpenAI's gym library.
  \item Updated from Euler's method to Runge-Kutta.
  \item Applied an LQR control scheme to keep the pendulum upright.
\end{compactItemize}
\medskip

\project{Android App -- Family History Map}{Summer 2018}
\begin{compactItemize}
  \item Wrote both the client and server in Java.
  \item Displayed family history data with a Google MapFragment.
  \item Implemented activities for log-in, map interaction, life event details, and app settings.
  \item Wrote the SQL commands that the server would use to store and retrieve user data.
\end{compactItemize}

\begin{comment}
  TODO:
  -Macro command for courses list.
  -Push macros into other file (lsResume.sty)
  -Projects:
    >

      \subsection*{Graph-Based Image Segmentation}
  \subsection*{SVD Image Compression}
  \subsection*{Facial Recognition with Eigenfaces}
  \subsection*{Applications of PageRank Algorithm}
  \subsection*{Drazin Inverse for Social Network Link Prediction}
  \subsection*{Jacobi, Gauss-Seidel, and Successive Over-Relaxation for Solving Linear Systems}
  \subsection*{Linked Lists}
  \subsection*{Binary Search Trees}
  \subsection*{K-D Trees for K-Nearest Neighbors}
  \subsection*{Breadth First Search and Six Degrees of Kevin Bacon}
  \subsection*{Random Speech Generation with Markov Chains}
  \subsection*{Simplex Method}
\end{comment}

\end{document}
